Binarity's effects on occurrence rates measured by transit surveys

### 2017-10-19 paper/model_2.tex
moving things around

The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
density is
\begin{equation}
\Lambda = \sum_i
\left[
\left(
    w_i \Lambda_i \int_{\Omega_{\rm desired}} p_i(\vec{x}) \,{\rm d}\Omega
\right)
\cdot
\left(
    w_i \Lambda_i \int_{\Omega_{\rm total}} p_i(\vec{x}) \,{\rm d}\Omega
\right)^{-1}
\right]
\end{equation}
for a desired volume of phase space $\Omega_{\rm desired}$.
Specifying the desired mass ratios of interest as $q_{\rm min} < q < q_{\rm 
max}$, this simplifies to
\begin{equation}
\Lambda = 
\frac{N_0 \Lambda_0 + N_1 \Lambda_1 + N_2 \Lambda_2 f_2}
{N_{\rm tot}},
\end{equation}
for
\begin{equation}
f_2 \equiv
\left(
\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q
\right)
\cdot
\left(
\int_{0}^{1} p_2(q) \,{\rm d}q
\right)^{-1}.
\end{equation}

>>>>

The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
density for a desired volume of phase space $\Omega_{\rm desired}$ is given by 
Eq.~\ref{eq:occ_rate}.
Specifying the desired mass ratios of interest as $q_{\rm min} < q < q_{\rm 
max}$, this simplifies to
\begin{equation}
\Lambda = 
\frac{N_0 \Lambda_0 + N_1 \Lambda_1 + N_2 \Lambda_2 f_2}
{N_{\rm tot}},
\end{equation}
for
\begin{equation}
f_2 \equiv
\left(
\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q
\right)
\cdot
\left(
\int_{0}^{1} p_2(q) \,{\rm d}q
\right)^{-1}.
\end{equation}
